Draft

### 2016-10-30 Draft/sections/misc-math.tex
New notes in Draft, about a specific function.

$\triangle \cdot 2 = \triangle$, What will be of $\triangle + 1$?

>>>>

$\triangle \cdot 2 = \triangle$, What will be of $\triangle + 1$?
\subsection{Funcation satisfying \texorpdfstring{$f(x+y)=f(x)f(x)$}{}}
\label{sec:Funcation satisfying \texorpdfstring{$f(x+y)=f(x)f(x)$}{}}

Here I prove a simple fact that:
\begin{thm}
    Any smooth $f$ function of $\mathbb{R}$. If $f$ satisfy the
    relation:
    \begin{equation}
        f(x+y)=f(x)f(y)
    \end{equation}
    for any $x,y\in \mathbb{R}$, and $f(0)\neq 0$. Then:
    \begin{equation}
        f(x) = e^{k x}
    \end{equation}
    where $k=\dv{f}{x}\left(0\right)$.
\end{thm}
\begin{proof}
    Notice that since $f(0)=f(0+0)=f(0)^2$, and $f(0)\neq 0$, we have
    $f(0)=1$.

    Consider
    \begin{align*}
        \dv{f}{x} = \lim_{\Delta x\to 0} 
        \frac{f(x+\Delta x)-f(x)}{\Delta x}
            = \lim_{\Delta x\to 0} 
            \frac{f(x)\left(f(\Delta x)-1\right)}{\Delta x}
    \end{align*}
    Using Taylor expansion about $f(0)$ and notice $f(0)=1$, one will
    easily get
    \begin{equation*}
        \lim_{\Delta x\to 0} 
            \frac{f(\Delta x)-1}{\Delta x}
            = f'(0)
    \end{equation*}
    Therefore, 
    \begin{equation*}
        \dv{f}{x} = f'(0)f(x)
    \end{equation*}
    Hence by thoey of differential equations (I don't quite remember
    the specific theorem), one has $f(x)=e^{f'(0)x}$.
\end{proof}
